Results

### 2018-11-23 Manuscript_draft/Results.Rmd
Other NMDS from other package

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
library(ggfortify)
library(ggplot2)
library(stats)
library(cluster)
#load environment
load("myEnvironment_mantel.RData")
```

@@

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
library(ggfortify)
library(ggplot2)
library(stats)
library(cluster)
library(MASS)
#load environment
load("myEnvironment_mantel.RData")
```

@@

\newpage
Now I use non metric multidimensional scaling for all the traits of our species. The traits used are: Stigma_type, Selfing_rate, Pollem_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, cache.comments=FALSE,results='hide',fig.keep='all'}
all <- read.csv("Data/traits_all.csv", sep=",")
rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
all <- all[,-c(1,2,10,13)]
all_scaled <- scale(all)
all_scaled_dist <- dist(all_scaled)
autoplot(sammon(all_scaled_dist), shape = FALSE, main="Non-metric multidimensional scaling",label.colour = 'blue', label.size = 3)
```

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, cache.comments=FALSE, results='hide'}
all <- read.csv("Data/traits_all.csv", sep=",")
rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
spp=c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
all <- all[,-c(1,2,10,13)]
#In this case we consider all the traits. 
NMDS=metaMDS(all,k=2,trymax=100)
ordiplot(NMDS,type="n")
orditorp(NMDS,display="sites",col=c(rep("green",2),"blue","green", rep("black",2),"blue","green", rep("blue",2)),
         air=0.01,cex=1.25)
```
